Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays

### 2021-11-24 PrevAdjSurvey.tex
Updates from Overleaf

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_005_prev}
\caption{CAPTION HERE.}
\label{fig:perfect_confidence_interval_width_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_05_prev}
\caption{CAPTION HERE.}
\label{fig:perfect_confidence_interval_width_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_005_prev}
\caption{CAPTION HERE.}
\label{fig:perfect_confidence_interval_width_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_05_prev}
\caption{CAPTION HERE.}
\label{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_005_prev}
\caption{CAPTION HERE.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_05_prev}
\caption{CAPTION HERE.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_005_prev}
\caption{CAPTION HERE.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_05_prev}
\caption{CAPTION HERE.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}
\end{figure}
